Incorporating individual variation in animal movement models

### 2021-02-15 movement_paper/2_11_explora.Rmd
exploring home range stuff.

>>>>

## Home range

```{r}
# Use only ones with more than 40 locations

aracari_data %>% 
  group_by(animal_id) %>% 
  tally() %>% 
  filter(., n >= 38) %>%
  dplyr::select(., animal_id) ->ids

aracari_sp <- aracari_data %>% 
  filter(., animal_id %in% ids$animal_id) %>% 
  dplyr::select(., animal_id, x, y) %>% 
  rename(id = animal_id)

coordinates(aracari_sp) <- c("x", "y")
proj4string(aracari_sp) <- CRS("+proj=utm +zone=18 +datum=WGS84")

library(adehabitatHR)
aracari_mcp <- mcp(aracari_sp, percent = 95)
aracari_mcp
plot(aracari_mcp)

# Kernel
kernel_ref <- kernelUD(aracari_sp)
image(kernel_ref)

aracari_kernel_poly <- getverticeshr(kernel_ref, percent = 95)
print(aracari_kernel_poly)
